CDSR Human Data/Modelling Paper

### 2013-09-11 code/scenarios/cdsr/trunk/papers/ACS2013/main.tex
JK updated table 2 by removing t-test results

The long-term goal of this work is to create of agents that can naturally interact with people in human environments.  While the study presented below illustrates the importance of context, object types and configurations, on human spatial judgements, constructing a cognitive systems approach requires more than reproducing these results.  First, the representational approach should be transferable to new situations.  While humans do not demonstrate mastery after a single example of concept, they are able to begin using it immediately refining it over time.  Second, the representation should be applicable in different reasoning tasks.  The functional nature of these regions makes them important for many tasks from action planning to activity recognition.

\section{Human Studies - John}

@@

The study was designed to examine the following questions about spatial regions:
\begin{enumerate}
	\item Given a particular situation how well do people agree on the location and extent of a named spatial region?
	\item Does the orientation and location of objects (with relevant functional semantics) in a given situation effect the location and extent of a named spatial region?
\end{enumerate}

To examine these questions we developed three different trials. In all three trial types the subject was presented with a visual stimuli (such as a room floor plan or a map) and an accompanying linguistic description (such as \emph{go to the front of the room}, however the way the task the subject was set varied across the trials:
\begin{enumerate}
	\item Trial type 1: the subject was asked to draw a polygon that defined the extent of the spatial region described in the description or to select a no region option.
	\item Trial type 2: a location was marked on the visual stimuli (using a red dot) and the subject was asked to rank on a five point likert scale their judgement of how well the location matched the described spatial region.  
	\item Trial type 3: subjects were asked to mark on the visual stimuli, by clicking with the mouse, the location that they felt was most prototypical of the spatial description. 
\end{enumerate}

All three trial types use the same visual stimuli and accompanying spatial descriptions. Figure \ref{fig:exp_stimuli} presents the stimuli used in the experiment. Throughout the rest of the paper we will use the labels from Figure \ref{fig:exp_stimuli} as the names for the different stimuli. The stimuli can be broken into three groups based on the domain and the spatial region that accompanied them: the classroom domain stimuli were always accompanied by the spatial description \emph{the front of the classroom}; the geographical map stimuli were always accompanied by the description \emph{the bottleneck}; and the military engagement stimuli were always accompanied by the description \emph{safety}.

The classroom stimuli consisted of pairs of floor plans and photos of classrooms with different chair configurations. For example, Figure \ref{fig:classroom-a} is a floor plan of a classroom where the chairs have been arranged in a circle and Figure \ref{fig:classroom-b} is the accompanying photo of this classroom. We developed four different classroom stimuli each with a different layout of chairs: a circular chair layout, a U shaped layout (Figure \ref{fig:classroom-c} and Figure \ref{fig:classroom-d}), a prototypical layout with the chairs close to the expected front of the room (Figure \ref{fig:classroom-e}), and a prototypical layout with the chairs far away from the expected front of the room (Figure \ref{fig:classroom-f})\footnote{In the interest of saving space we do not show all the classroom photo stimuli}. To control for left-right bias effects two versions of the U shaped layout, close rows layout and far rows layout were created by horizontally flipping the layouts. Conseqeuntly, there were 7 classroom stimuli (circle, U $\times 2$, close $\times 2$, far $\times 2$). In designing these stimuli we deliberately chose some layouts that were very prototypical or close variations on standard layouts - e.g., Figures \ref{fig:classroom-e} and \ref{fig:classroom-f} - and others were more novel - Figure \ref{fig:classroom-a} and \ref{fig:classroom-c}. By varying the prototypicality of the layouts we hoped to get some variation across the between subject agreement on a per stimuli basis, for example we expected to get a higher between subject agreement for the stimuli that were more prototypical. This would provide insight into research question 1, in particular it would point to the effect of prototypicality on the semantics of contextually defined spatial regions. Also, because the prototypicality of the scenes was varied by adjusting the location and orientation of objects in the scenes, a variation in agreement across the stimuli would provide evidence that the orientation and location of objects do effect the location and extent of spatial regions.

@@

\subsection{Participants and Procedure}

43 undergraduate students from two different third level institutes took part in the study. To control for sequence effects the presentation order of the trials were randomised each participant. Also in order to minimise fatigue of the subjects for the Type 2 Likert trials each subject only ranked a randomly selected subset of the trials.

\subsection{Analysis}

@@

One well known metric for analysising interannotator agreement is the \textbf{Cohen's kappa coefficient}, $\kappa$. Cohen's kappa measures the agreement between two annotators who each classify a number of items into two or more mutually exclusive classes. $\kappa$ ranges from 0 indicating no agreement beyond chance to 1 indicating complete agreement. In order to use Cohen's kappa to measure the agreement between subject responses in our type 1 trials we generated a set of 47,000 test points that were uniformly distribute across each stimuli and used each subject's polygon to classify the test points as being inside or outside the polygon. After classifying the test points for each subject we then computed an average pairwise kappa score for each subject with all the other subjects on a per stimuli basis. In this calculation if either of the subjects in a pair entered a no region response for a particular stimuli a $\kappa$ value of 0 was used. Figure \ref{fig:subj-kappa} shows a histogram of the per subject average kappa scores using ten equal width intervals covering the $\kappa$ range between 0 and 1.  It is evident from this figure that most subjects had a $\kappa$ score between $0.2-0.5$ with a overall majority of subjects having a $\kappa$ score between $0.3-0.4$. A $\kappa$ score between $0.3-0.4$ would be considered as being poor to fair. This would indicate that there was some agreement between subjects but less that would be expected. However, this calculation was done across all the stimuli and as we have already mentioned some of the stimuli were deliberately designed to be non-prototypical, in particular we expected the classroom stimuli where the chairs were arranged in a circle (Figure \ref{fig:classroom-a}) and in a U shaped pattern (Figure \ref{fig:classroom-c} and its horizontally flipped equivalent) to be relatively novel situations for the subjects. Indeed, if we look at the histogram of the average pairwise $\kappa$ scores by stimuli, Figure \ref{fig:stim-kappa}, it is evident that there is a large variation, ranging from $0$ to $0.8$, in $\kappa$ scores for each stimuli. In more detail, Table \ref{tab:stimuli-kappa-scores} lists the average pairwise $\kappa$ score for each of the visual stimuli used in the experiment and the number of no regrion responses for each stimuli. It is clear from this table that the non-prototypical stimuli have the lowest $\kappa$ scores and also that there is relationship between typicality and the number of no region responses. Given this relatively large variation across stimuli, which we attribute to the prototypicality of the depicted situation, we computed the average pairwise $\kappa$ scores for each subject when the non-prototypical stimuli trials were excluded. Figure \ref{fig:subj-kappa-proto} presents the histogram of the resulting average pairwise subject  $\kappa$ scores by subject. Not surpringly, with the exclusion on the non-prototypical stimuli the average pairwise $\kappa$ scores increase, with over half the subjects having an average pairwise $\kappa$ score between $0.4$ and $0.6$. $\kappa$ scores in this range can to interpreted as fair to good.

The analysis of the type 1 trials indicates that, over a range of domains and spatial regions, the responses from the subjects did agree, to a good degree. Furthermore, there results support the hypothesis that the defintion of spatial regions in a given context is effected by the location and orientation of objects in the context. For example, focusing on the classroom scenes (stimuli, $a$, $c$, $e$, and $f$) the only difference between these trials was the layout of the chairs in the room and yet there is a substantial variation across these stimuli of the agreement between subjects on the specified spatial region, namely \textit{the front of the room}. Situation $f$ resulted in an average pairwise agreement of $0.393$ and in comparision situation $a$ had an average pairwise agreement of $0.0996$.

The type 2 trials the same visual stimuli and accompanying spatial descriptions as the type 1 trials with the addition that a location was marked on the visual stimuli (using a red dot) and the subject was asked to rank on a five point likert scale their judgement of how well the location matched the described spatial region. For each stimuli domain (classroom, map, military engagement) three points (P1, P2, and P3) were pre-selected.

The location of these points was informed by the results of a pilot study and the final design of the study and they were positioned such that for each particular stimuli one of the domain's points, called the \textbf{sweetspot}, was located near the expected prototypical center of the described spatial region. In the classroom domain the three points were located along the horizontal line that bisected the stimuli with P1 positioned on the left of the stimuli, P2 in the center and P3 on the right of the stimuli (as shown in Figure \ref{fig:classroom-points}). One of the aims of this configuration of points was to provide comparable data points between the trials where the classroom stimuli were horizontally flipped. In the classroom domain the expected sweetspot varied between the points depending on the stimuli. In the map domain P1 was positioned in the top left corner of the stimuli,  P2 was the expected sweetspot and was located within the expected bottleneck region for both stimuli and P3 was located in the bottom right corner of the stimuli (see Figure \ref{fig:bottleneck-points}).  In the military engagement domain the three test points were located on the vertical line that bisected the stimuli: P1 was located near the top of the image in the proximity of the enemy tanks, P2 was located near the center of the image such that in some stimuli it was in a no-man's land position and in other stimuli (specifically stimuli (i) in the friendly tanks have moved forward and (l) where there is an extra friendly turret) it could be considered to be in a protected area, and P3 was located near the bottom of the stimuli and consequently was always located behind the friendly tanks/turrets. P3 was the expected sweetspot in the military engagement domain but it was also hoped that P2 rating would differ between the stimuli where it was in no-mans land and where it recieved some protection.

@@

\begin{table}
\centerline{
\begin{tabular}{l c c c l}
\hline
Domain & \multicolumn{4}{c}{Map/Bottleneck} \\
 ~ & \multicolumn{3}{c}{Average Likert Rating} & Sweetspot Rated Significantly Higher? \\
Stim ID & P1 & P2 & P3 & One-Tailed Two Sample T-Test with $\alpha=0.05$, $H_0:\mu(P_i)=\mu(P_j)$\\
(g) & $1.1707$ & $\mathbf{4.6667}$ & $1.85$ & $H_A:\mu(P2)>\mu(P1),~p<2.2^{-16};~H_A:\mu(P2)>\mu(P3),~p<2.2^{-16}$\\ % 1_1
(h) & $1.1707$ & $\mathbf{4.7561}$ & $1.585$ & $H_A:\mu(P2)>\mu(P1),~p<2.2^{-16};~H_A:\mu(P2)>\mu(P3),~p<2.2^{-16}$\\ % 1_2
\\
\hline
Domain & \multicolumn{4}{c}{Classrom/Front of Room} \\
 ~ & \multicolumn{3}{c}{Average Likert Rating} & Sweetspot Rated Significantly Higher? \\
Stim ID & P1 & P2 & P3 & One-Tailed Two Sample T-Test with $\alpha=0.05$, $H_0:\mu(P_i)=\mu(P_j)$\\
(a) & $\mathbf{3.5122}$ & $2.6341$ & $1.9024$ & $H_A:\mu(P1)>\mu(P2),~p=6.497^{-4};~H_A:\mu(P1)>\mu(P3),~p=4.073^{-8}$\\ % 2_1
(c) & $\mathbf{4.7073}$ & $2.9024$ & $1.3571$ & $H_A:\mu(P1)>\mu(P2),~p=6.396^{-16};~H_A:\mu(P1)>\mu(P3),~p<2.2^{-16}$\\ % 2_6
(c-flipped) & $1.244$ & $2.9268$ & $\mathbf{4.6429}$ & $H_A:\mu(P3)>\mu(P1),~p<2.2^{-16};~H_A=\mu(P3)>\mu(P2),~p:1.864^{-12}$\\ %2_7
(e) & $\mathbf{4.7561}$ & $2.0000$ & $1.2439$ & $H_A=\mu(P1)>\mu(P2),~p<2.2^{-16};~H_A=\mu(P1)>\mu(P3):~p<2.2^{-16}$\\ %2_2
(e-flipped) & $1.2439$ & $1.8500$ & $\mathbf{4.7073}$ & $H_A=\mu(P3)>\mu(P1),~p<2.2^{-16};~H_A=\mu(P3)>\mu(P2):~p<2.2^{-16}$\\ % 2_3
(f) & $\mathbf{4.8292}$ & $2.0976$ & $1.2750$ & $H_A=\mu(P1)>\mu(P2),~p<2.2^{-16};~H_A=\mu(P1)>\mu(P3),~p<2.2^{-16}$\\ % 2_4
(f-flipped) & $1.1463$ & $2.3171$ & $\mathbf{4.6585}$ & $H_A=\mu(P3)>\mu(P1),~p<2.2^{-16};~H_A=\mu(P3)>\mu(P2),~p<2.2^{-16}$\\ % 2_5
\\
\hline
Domain & \multicolumn{4}{c}{Military Engagement/Safe Region} \\
 ~ & \multicolumn{3}{c}{Average Likert Rating} &  Sweetspot Rated Significantly Higher?\\
Stim ID & P1 & P2 & P3 & One-Tailed Two Sample T-Test with $\alpha=0.05$, $H_0:\mu(P_i)=\mu(P_j)$\\
(i) & $1.1951$ & $4.3902$ & $\mathbf{4.9024}$ & $H_A=\mu(P3)>\mu(P1),~p<2.2^{-16};~H_A=\mu(P3)>\mu(P2),~p=5.382^{-4}$\\ % 3_1
(j) & $1.0952$ & $2.2927$ & $\mathbf{4.5122}$ & $H_A=\mu(P3)>\mu(P1),~p<2.2^{-16};~H_A=\mu(P3)>\mu(P2),~p<7.981^{-14}$\\ % 3_2
(k) & $1.0714$ & $2.7804$ & $\mathbf{4.6585}$ & $H_A=\mu(P3)>\mu(P1),~p<2.2^{-16};~H_A=\mu(P3)>\mu(P2),~p=2.708^{-13}$\\ % 3_3
(l) & $1.2327$ & $3.1667$ & $\mathbf{4.7073}$ & $H_A=\mu(P3)>\mu(P1),~p<2.2^{-16};~H_A=\mu(P3)>\mu(P2),~p=6.621^{-12}$\\ % 3_4
\\
\hline
\hline
\end{tabular}
}
\label{tab:point-likert-scores}
\caption{Average Likert Ratings per Point by Domain with T-Test results: in all cases the average rating of the sweetspot is significantly higher than the other points tested for that stimuli}
\end{table}

>>>>

The long-term goal of this work is to create intelligent agents that can naturally interact with people in human environments.  While the study presented below illustrates the importance of context, object types and configurations, on human spatial judgements, constructing a cognitive systems approach requires more than reproducing these results.  First, the representational approach should be transferable to new situations.  While humans do not demonstrate mastery after a single example of a concept, they are able to begin using it immediately refining it over time.  Second, the representation should be applicable in different reasoning tasks.  The functional nature of these regions makes them important for many tasks from action planning to activity recognition.

\section{Human Studies}

@@

The study was designed to examine the following questions about spatial regions:
\begin{enumerate}
	\item Given a particular situation how well do people agree on the location and extent of a named context dependent spatial region?
	\item Does the orientation and location of objects (with relevant functional semantics) in a given situation effect the location and extent of a named context dependent spatial region?
\end{enumerate}

To examine these questions, we developed a set of visual stimuli depicting a human environment (such as a room floor plan or a map) each paired with an accompanying linguistic description of a CDSR easily understood within the context of that environment (such as \emph{go to the front of the room}).  Figure \ref{fig:exp_stimuli} presents the stimuli used in the experiment. Throughout the rest of the paper we will use the labels from Figure \ref{fig:exp_stimuli} as the names for the different stimuli. The stimuli can be broken into three groups based on the domain and the spatial region that accompanied them: (1) the classroom domain stimuli were always accompanied by the spatial description \emph{the front of the classroom}; (2) the geographical map stimuli were always accompanied by the description \emph{the bottleneck}; and (3) the military engagement stimuli were always accompanied by the description \emph{safety}.

The classroom stimuli consisted of pairs of floor plans and photos of classrooms with different chair configurations. For example, Figure \ref{fig:classroom-a} is a floor plan of a classroom where the chairs have been arranged in a circle and Figure \ref{fig:classroom-b} is the accompanying photo of this classroom. We developed four different classroom stimuli each with a different layout of chairs: a circular chair layout, a U shaped layout (Figure \ref{fig:classroom-c} and Figure \ref{fig:classroom-d}), a typical row-based layout with the first row of chairs close to the expected front of the room (Figure \ref{fig:classroom-e}), and the same arrangement with the front row of chairs further away from the expected front of the room (Figure \ref{fig:classroom-f})\footnote{In the interest of saving space we do not show all the classroom photo stimuli}. To control for left-right bias effects two versions of the U shaped layout, close rows layout and far rows layout were created by horizontally flipping the layouts. Conseqeuntly, there were 7 classroom stimuli (circle, U $\times 2$, close $\times 2$, far $\times 2$). In designing these stimuli we deliberately chose some layouts that were very common or close variations on standard layouts - e.g., Figures \ref{fig:classroom-e} and \ref{fig:classroom-f} - and others were more novel - Figure \ref{fig:classroom-a} and \ref{fig:classroom-c}. By varying the typicality of the layouts we hoped to get some variation across the between subject agreement on a per stimuli basis, for example we expected to get a higher between subject agreement for the stimuli that were more common. This would provide insight into research question 1, in particular it would point to the effect of typicality on the semantics of contextually defined spatial regions. Also, because the typicality of the scenes was varied by adjusting the location and orientation of objects in the scenes, a variation in agreement across the stimuli would provide evidence that the orientation and location of objects do effect the location and extent of spatial regions.

@@

\subsection{Participants and Procedure}
Using these stimuli pairs, we developed an online experiment with two different types of trials to explore our initial questions. 43 undergraduate students from two different third level institutes took part in the study. To control for sequence effects the presentation order of the trials were randomised for each participant as was the order of the stimuli presented within each trial.

\subsection{Trial Type 1 - Design}
In the first set of trials, the subject was asked to draw a polygon that defined the extent of the CDSR given or to select a no region option.  The drawing was done on the diagram in all stimuli with the classroom photographs provided for reference in those trials.  Subjects drew polygons by clicking to position the verticies with lines being automatically generated between each point indicated as the subject drew.  There was no upper bound placed on the number of line segments drawn but subjects were required to provide at least three line segments or to choose no region before continuing to the next stimulus.

\subsection{Trial Type 1 - Results}
One well known metric for analysising interannotator agreement is the \textbf{Cohen's kappa coefficient}, $\kappa$. Cohen's kappa measures the agreement between two annotators who each classify a number of items into two or more mutually exclusive classes. $\kappa$ ranges from 0 indicating no agreement beyond chance to 1 indicating complete agreement. In order to use Cohen's kappa to measure the agreement between subject responses in our type 1 trials we generated a set of 47,000 test points that were uniformly distributed across each stimuli and used each subject's polygon to classify the test points as being inside or outside the polygon. After classifying the test points for each subject we then computed an average pairwise kappa score for each subject with all the other subjects on a per stimuli basis. In this calculation if either of the subjects in a pair entered a no region response for a particular stimuli a $\kappa$ value of 0 was used. Figure \ref{fig:subj-kappa} shows a histogram of the per subject average kappa scores using ten equal width intervals covering the $\kappa$ range between 0 and 1.  It is evident from this figure that most subjects had a $\kappa$ score between $0.2-0.5$ with a overall majority of subjects having a $\kappa$ score between $0.3-0.4$. A $\kappa$ score between $0.3-0.4$ would be considered as being poor to fair. This would indicate that there was some agreement between subjects but less that would be expected. However, this calculation was done across all the stimuli and as we have already mentioned some of the stimuli were deliberately designed to be non-prototypical, in particular we expected the classroom stimuli where the chairs were arranged in a circle (Figure \ref{fig:classroom-a}) and in a U shaped pattern (Figure \ref{fig:classroom-c} and its horizontally flipped equivalent) to be relatively novel situations for the subjects. Indeed, if we look at the histogram of the average pairwise $\kappa$ scores by stimuli, Figure \ref{fig:stim-kappa}, it is evident that there is a large variation, ranging from $0$ to $0.8$, in $\kappa$ scores for each stimuli. In more detail, Table \ref{tab:stimuli-kappa-scores} lists the average pairwise $\kappa$ score for each of the visual stimuli used in the experiment and the number of no regrion responses for each stimuli. It is clear from this table that the non-prototypical stimuli have the lowest $\kappa$ scores and also that there is relationship between typicality and the number of no region responses. Given this relatively large variation across stimuli, which we attribute to the prototypicality of the depicted situation, we computed the average pairwise $\kappa$ scores for each subject when the non-prototypical stimuli trials were excluded. Figure \ref{fig:subj-kappa-proto} presents the histogram of the resulting average pairwise subject  $\kappa$ scores by subject. Not surpringly, with the exclusion on the non-prototypical stimuli the average pairwise $\kappa$ scores increase, with over half the subjects having an average pairwise $\kappa$ score between $0.4$ and $0.6$. $\kappa$ scores in this range can to interpreted as fair to good.

The analysis of the type 1 trials indicates that, over a range of domains and spatial regions, the responses from the subjects did agree, to a good degree. Furthermore, their results support the hypothesis that the defintion of CDSRs in a given context is effected by the location and orientation of objects in the environment. For example, focusing on the classroom scenes (stimuli, $a$, $c$, $e$, and $f$) the only difference between these trials was the layout of the chairs in the room and yet there is a substantial variation across these stimuli of the agreement between subjects on the specified spatial region, namely \textit{the front of the room}. Situation $f$ resulted in an average pairwise agreement of $0.393$ and in comparision situation $a$ had an average pairwise agreement of $0.0996$.

\subsection{Trial Type 2 - Design} 
In the second set of trials, a location was marked on the visual stimuli (using a red dot) and the subject was asked to rank on a five point likert scale their judgement of how well the location matched the described spatial region.  The location of these points was informed by the results of a pilot study and the final design of the study and they were positioned such that for each particular stimuli one of the domain's points, called the \textbf{sweetspot}, was located near the expected prototypical center of the described spatial region. In the classroom domain the three points were located along the horizontal line that bisected the stimuli with P1 positioned on the left of the stimuli, P2 in the center and P3 on the right of the stimuli (as shown in Figure \ref{fig:classroom-points}). One of the aims of this configuration of points was to provide comparable data points between the trials where the classroom stimuli were horizontally flipped. In the classroom domain the expected sweetspot varied between the points depending on the stimuli. In the map domain P1 was positioned in the top left corner of the stimuli,  P2 was the expected sweetspot and was located within the expected bottleneck region for both stimuli and P3 was located in the bottom right corner of the stimuli (see Figure \ref{fig:bottleneck-points}).  In the military engagement domain the three test points were located on the vertical line that bisected the stimuli: P1 was located near the top of the image in the proximity of the enemy tanks, P2 was located near the center of the image such that in some stimuli it was in a no-man's land position and in other stimuli (specifically stimuli (i) in the friendly tanks have moved forward and (l) where there is an extra friendly turret) it could be considered to be in a protected area, and P3 was located near the bottom of the stimuli and consequently was always located behind the friendly tanks/turrets. P3 was the expected sweetspot in the military engagement domain but it was also hoped that P2 rating would differ between the stimuli where it was in no-mans land and where it recieved some protection.

\subsection{Trial Type 2 - Results}

@@

%The type 2 trials the same visual stimuli and accompanying spatial descriptions as the type 1 trials with the addition that a location was marked on %the visual stimuli (using a red dot) and the subject was asked to rank on a five point likert scale their judgement of how well the location matched %the described spatial region. For each stimuli domain (classroom, map, military engagement) three points (P1, P2, and P3) were pre-selected.

@@

\begin{table}
\centerline{
\begin{tabular}{l c c c }
\hline
Domain & \multicolumn{3}{c}{Map/Bottleneck} \\
 ~ & \multicolumn{3}{c}{Average Likert Rating} \\
Stim ID & P1 & P2 & P3 \\
(g) & $1.1707$ & $\mathbf{4.6667}$ \\ % 1_1
(h) & $1.1707$ & $\mathbf{4.7561}$ \\ % 1_2
\\
\hline
Domain & \multicolumn{3}{c}{Classrom/Front of Room} \\
 ~ & \multicolumn{3}{c}{Average Likert Rating} \\
Stim ID & P1 & P2 & P3 \\
(a) & $\mathbf{3.5122}$ & $2.6341$ & $1.9024$ \\ % 2_1
(c) & $\mathbf{4.7073}$ & $2.9024$ & $1.3571$ \\ % 2_6
(c-flipped) & $1.244$ & $2.9268$ & $\mathbf{4.6429}$ \\ %2_7
(e) & $\mathbf{4.7561}$ & $2.0000$ & $1.2439$ \\ %2_2
(e-flipped) & $1.2439$ & $1.8500$ & $\mathbf{4.7073}$ \\ % 2_3
(f) & $\mathbf{4.8292}$ & $2.0976$ & $1.2750$ \\ % 2_4
(f-flipped) & $1.1463$ & $2.3171$ & $\mathbf{4.6585}$ \\ % 2_5
\\
\hline
Domain & \multicolumn{3}{c}{Military Engagement/Safe Region} \\
 ~ & \multicolumn{3}{c}{Average Likert Rating} \\
Stim ID & P1 & P2 & P3\\
(i) & $1.1951$ & $4.3902$ & $\mathbf{4.9024}$ \\ % 3_1
(j) & $1.0952$ & $2.2927$ & $\mathbf{4.5122}$ \\ % 3_2
(k) & $1.0714$ & $2.7804$ & $\mathbf{4.6585}$ \\ % 3_3
(l) & $1.2327$ & $3.1667$ & $\mathbf{4.7073}$\\ % 3_4
\\
\hline
\hline
\end{tabular}
}
\label{tab:point-likert-scores}
\caption{Average Likert Ratings per Point by Domain.}
\end{table}

%\begin{table}
%\centerline{
%\begin{tabular}{l c c c l}
%\hline
%Domain & \multicolumn{4}{c}{Map/Bottleneck} \\
% ~ & \multicolumn{3}{c}{Average Likert Rating} & Sweetspot Rated Significantly Higher? \\
%Stim ID & P1 & P2 & P3 & One-Tailed Two Sample T-Test with $\alpha=0.05$, $H_0:\mu(P_i)=\mu(P_j)$\\
%(g) & $1.1707$ & $\mathbf{4.6667}$ & $1.85$ & $H_A:\mu(P2)>\mu(P1),~p<2.2^{-16};~H_A:\mu(P2)>\mu(P3),~p<2.2^{-16}$\\ % 1_1
%(h) & $1.1707$ & $\mathbf{4.7561}$ & $1.585$ & $H_A:\mu(P2)>\mu(P1),~p<2.2^{-16};~H_A:\mu(P2)>\mu(P3),~p<2.2^{-16}$\\ % 1_2
%\\
%\hline
%Domain & \multicolumn{4}{c}{Classrom/Front of Room} \\
% ~ & \multicolumn{3}{c}{Average Likert Rating} & Sweetspot Rated Significantly Higher? \\
%Stim ID & P1 & P2 & P3 & One-Tailed Two Sample T-Test with $\alpha=0.05$, $H_0:\mu(P_i)=\mu(P_j)$\\
%(a) & $\mathbf{3.5122}$ & $2.6341$ & $1.9024$ & $H_A:\mu(P1)>\mu(P2),~p=6.497^{-4};~H_A:\mu(P1)>\mu(P3),~p=4.073^{-8}$\\ % 2_1
%(c) & $\mathbf{4.7073}$ & $2.9024$ & $1.3571$ & $H_A:\mu(P1)>\mu(P2),~p=6.396^{-16};~H_A:\mu(P1)>\mu(P3),~p<2.2^{-16}$\\ % 2_6
%(c-flipped) & $1.244$ & $2.9268$ & $\mathbf{4.6429}$ & $H_A:\mu(P3)>\mu(P1),~p<2.2^{-16};~H_A=\mu(P3)>\mu(P2),~p:1.864^{-12}$\\ %2_7
%(e) & $\mathbf{4.7561}$ & $2.0000$ & $1.2439$ & $H_A=\mu(P1)>\mu(P2),~p<2.2^{-16};~H_A=\mu(P1)>\mu(P3):~p<2.2^{-16}$\\ %2_2
%(e-flipped) & $1.2439$ & $1.8500$ & $\mathbf{4.7073}$ & $H_A=\mu(P3)>\mu(P1),~p<2.2^{-16};~H_A=\mu(P3)>\mu(P2):~p<2.2^{-16}$\\ % 2_3
%(f) & $\mathbf{4.8292}$ & $2.0976$ & $1.2750$ & $H_A=\mu(P1)>\mu(P2),~p<2.2^{-16};~H_A=\mu(P1)>\mu(P3),~p<2.2^{-16}$\\ % 2_4
%(f-flipped) & $1.1463$ & $2.3171$ & $\mathbf{4.6585}$ & $H_A=\mu(P3)>\mu(P1),~p<2.2^{-16};~H_A=\mu(P3)>\mu(P2),~p<2.2^{-16}$\\ % 2_5
%\\
%\hline
%Domain & \multicolumn{4}{c}{Military Engagement/Safe Region} \\
% ~ & \multicolumn{3}{c}{Average Likert Rating} &  Sweetspot Rated Significantly Higher?\\
%Stim ID & P1 & P2 & P3 & One-Tailed Two Sample T-Test with $\alpha=0.05$, $H_0:\mu(P_i)=\mu(P_j)$\\
%(i) & $1.1951$ & $4.3902$ & $\mathbf{4.9024}$ & $H_A=\mu(P3)>\mu(P1),~p<2.2^{-16};~H_A=\mu(P3)>\mu(P2),~p=5.382^{-4}$\\ % 3_1
%(j) & $1.0952$ & $2.2927$ & $\mathbf{4.5122}$ & $H_A=\mu(P3)>\mu(P1),~p<2.2^{-16};~H_A=\mu(P3)>\mu(P2),~p<7.981^{-14}$\\ % 3_2
%(k) & $1.0714$ & $2.7804$ & $\mathbf{4.6585}$ & $H_A=\mu(P3)>\mu(P1),~p<2.2^{-16};~H_A=\mu(P3)>\mu(P2),~p=2.708^{-13}$\\ % 3_3
%(l) & $1.2327$ & $3.1667$ & $\mathbf{4.7073}$ & $H_A=\mu(P3)>\mu(P1),~p<2.2^{-16};~H_A=\mu(P3)>\mu(P2),~p=6.621^{-12}$\\ % 3_4
%\\
%\hline
%\hline
%\end{tabular}
%}
%\label{tab:point-likert-scores}
%\caption{Average Likert Ratings per Point by Domain with T-Test results: in all cases the average rating of the sweetspot is significantly higher than the other points tested for that stimuli}
%\end{table}
